Reconstructing Propositional Proofs in Type Theory

### 2017-11-21 paper/sections/introduction.tex
[ paper ] minor changes.

The proof-reconstruction tool \Athena was tested with \prg{GHC}~8.2.1.
Both libraries, \verb!agda-prop! and \verb!agda-metis! were tested with
\Agda~2.5.3 and \Agda standard library~0.14.
\Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
We successfully reconstruct around eighty theorems in classical propositional logic from the \TPTP
collection~\cite{Prieto-Cubides2017}.

>>>>

The proof-reconstruction tool \Athena was tested with \prg{GHC}~8.2.1.
Both libraries, \verb!agda-prop! and \verb!agda-metis! were tested with
\Agda~2.5.3 and \Agda standard library~0.14.
\Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
We successfully reconstruct around eighty theorems in classical propositional
logic from the \TPTP collection~\cite{Prieto-Cubides2017} to test
the developments and the formalization presented in this research.

### 2017-11-21 paper/sections/type-theory.tex
[ paper ] minor changes.

By following the Curry-Howard correspondence (see, for
example,~\cite{Wadler-2015}), types are propositions. The inhabitants
of that types, the \emph{terms}, are proofs of that propositions.
Since type theory is a formal system, we have a syntax and a set of
derivation rules. These rules enables us to derive a kind of
conclusions called \emph{judgments}. A judgment is another way to say
that a term has a certain type.

@@

We produce derivation trees inside the judgments using the derivation
rules. Since type theory can be seen as typed $λ$-calculus with
dependent function types, evaluation of $λ$-terms also called
\emph{normalization} of the proof- terms, are reductions using the
system inference rules.

@@

To reconstruct \Metis inference rules in type theory, we observed
that some rules or their inner functions are implemented by \emph{
general recursive} functions.

>>>>

By following the Curry-Howard correspondence (see, for
example,~\cite{Wadler-2015}), a formula corresponds to a \emph{type},
and one proof of that formula is a \emph{term} of the correspondent type.
Therefore, inhabitants types are such formulas with proofs, that is, theorems.

Since type theory is a formal system, we have a syntax and a set of
derivation rules. These rules enables us to derive a kind of
conclusions called \emph{judgments}. A judgment is another way to say
that a term has a certain type. Each term has associated a derivation,
we refer to this derivation as proof-terms.

@@

We produce derivation trees inside the judgments using the derivation
rules. Since type theory can be seen as typed $λ$-calculus with
dependent function types, evaluation of $λ$-terms also called
\emph{normalization} of the proof-terms, are reductions using the
system inference rules.

@@

To reconstruct \Metis inference rules in type theory, we observed
that some rules or their inner functions are implemented by
\emph{general recursive} functions.
